---
title: "CalCOFI seabird data formatting"
author: "Annie Schmidt"
date: "July 31, 2014"
output: html_document
---

This R markdown document contains code for formatting the CalCOFI seabird data survey into consistent format to include in our Marine CitiSci database
```{r load packages}
# Load libraries needed
library(stringr)

```
Load data
```{r load data}
# Load CalCOFI seabird observations
# Change path to point to your data file
cc_obs <- read.csv("/Users/aeschmidty/Google Drive/OSS Marine Project/Data/Bird and Mammal Census - CalCOFI cruises.csv",header=TRUE)
# Check that data loaded correctly
head(cc_obs)
tail(cc_obs)
summary(cc_obs)
names(cc_obs)

# Remove periods from column names
names(cc_obs)<-gsub("[.]", "", names(cc_obs))

# Load CalCOFI transect data
cc_trans<- read.csv("/Users/aeschmidty/Google Drive/OSS Marine Project/Data/Bird and Mammal Census Log - CalCOFI cruises.csv",header=TRUE)
# Check that data loaded correctly
head(cc_trans)
tail(cc_trans)
summary(cc_trans)
names(cc_trans)

# replace column headings
# Remove periods from column names
names(cc_trans)<-gsub("[.]", "", names(cc_trans))
names(cc_trans)<-gsub("[ยบ]","", names(cc_trans))
# names(cc_trans)<-gsub("[expression(~degree)]","", names(cc_trans))
names(cc_trans)

cc_trans$GISkey <- as.character(cc_trans$GISkey)

tm <- merge(cc_obs,cc_trans, by = "GISkey")

cc_trans[cc_trans$"GISkey"=="CAC19870502F12",]
```

# pull GIS.key from transect table
# find table of AOU alpha codes
# add columns for Genus and species
# add other columns to make consistent with mega database?
You can also embed plots, for example:

```{r, echo=FALSE}
plot(cars)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
